The Work Plan for the project is intended to outline the envisioned timeline to achieve the objectives set out for this project. The timeline is subjective to change based on the progress made and feedback received in the earlier stages of our research.

For modeling purposes, we will be using the integrated tool environment UPPAAL that allows for the modeling, verification, and validation of real-time systems modeled as networked timed automata~\cite{behrmann2004_Tutorial_UPPAAL}. UPPAAL is freely available only for research purposes\footnote{http://www.uppaal.org/} within the academia.

The timeline for the project is divided into four primary phases. These phases involve, notably, Literature Review and Initial Testing, System Modeling and Simulation, Data Analysis, and Assessment. Each phase will end with either a discussion with the course instructor or a research presentation and the feedback received from those events will be taken into account in the subsequent phases.

The first phase will focus primarily on identifying additional research questions by an extensive literature review of botnet behaviors and previous attempts to model such behavior using various modeling techniques. Concurrently, we will explore the capabilities of the UPPAAL modeling tool, create an initial system model to perform some initial simulations to meet the instructor for a detailed discussion two weeks before the progress presentation. The progress made up until that point, coupled with the feedback from the discussion, will direct our future activities and, if necessary, a shift in research focus.

Phase two will emphasize enhancing model accuracy and experimentation. We should be fairly certain about our final research goal at this point, which will be reflected by a more concentrated literature search closely aligning with our final goal. This phase ends with the progress presentation in early November.

In the third phase, we will prioritize analyzing the experimental results and verifying some of the reachability properties of the system. The results from this stage might also engender modified experiments and small changes in the model to accommodate those modifications. This phase will also end with a discussion with the instructor, determining if an extension of the scope is feasible before the presentation of the results in early December.

The final phase will focus almost exclusively on the writing and finalizing the assessment of our experimental results to provide feasible recommendations. Additionally, this phase will include rigorous scrutiny of each group member's written work by the other to deliver a high-quality piece of work by the end of the project deadline.
